---
title: "DOI-package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{DOI-package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(doipkg)
```

This package can be used to simulate how social network intervention can affect a specific outcome by adopting digital technology.

# Fun 1: Simulate social network data

This function generates a dataset with multiple characteristics and creates an adjacent matrix to generate a network.

### Function

generate_network_matrices(num_agents)

### Arguments

|              |                                                              |
|----------------|-------------------------------------------------------|
| `num_agents` | A numeric scalar indicates the number of agents to generate. |

## Fun 2: Calculate the distance between agents

Computes the similarity or distance between two numeric vectors based on a specified method.

### Function

calculate_distance(individual1, individual2, method)

### Arguments

|               |                                                                                          |
|---------------|---------------------------------------------------------|
| `individual1` | Numeric vector. The first individual.                                                    |
| `individual2` | Numeric vector. The second individual.                                                   |
| `method`      | String. The method used for calculation: "Cosine", "Hamming", "Euclidean", or "Jaccard". |

## Fun 3: Determine adopters

This function determines adopters in a network using one of three centrality measures: counts, betweenness, or closeness.

### Function

determine_adopter( total_n, adj_matrix, final_matrix, indices, p_innovators, approach )

### Arguments

|                |                                                                                           |
|---------------|---------------------------------------------------------|
| `total_n`      | Numeric scalar. Total number of nodes in the network.                                     |
| `adj_matrix`   | Numeric matrix. The adjacency matrix representing the network.                            |
| `final_matrix` | Numeric matrix. An additional matrix related to the network (optional for this function). |
| `indices`      | Numeric vector. Indices of the nodes to consider for adoption.                            |
| `p_innovators` | Numeric scalar. Proportion of total nodes to be classified as innovators.                 |
| `approach`     | String. The centrality method to use: "counts", "betweeness", or "closeness".             |

## Fun 4: Simulate the process for determining adopters at different diffusion process

This function identifies adopters across multiple stages based on centrality measures, updates their efficacy, and adjusts data for non-adopters.

### Function

detect_adopters( num_agents, adj_matrix, final_matrix, original_data, stages, stages_name, ps_theory, adoption_efficacy, non_adoption_efficacy, approach, p_prior )

### Arguments

|                         |                                                                                 |
|------------------|------------------------------------------------------|
| `num_agents`            | Numeric scalar. Total number of agents in the network.                          |
| `adj_matrix`            | Numeric matrix. Adjacency matrix representing the network.                      |
| `final_matrix`          | Numeric matrix. Additional network-related matrix (optional for this function). |
| `original_data`         | Numeric matrix. Data containing baseline and other attributes for agents.       |
| `stages`                | List. A sequence of stages for the adoption process.                            |
| `stages_name`           | List. Names corresponding to each stage.                                        |
| `ps_theory`             | List. Proportions of adopters for each stage.                                   |
| `adoption_efficacy`     | List. Efficacy values added for adopters at each stage.                         |
| `non_adoption_efficacy` | Numeric scalar. Efficacy value for non-adopters.                                |
| `approach`              | String. Centrality measure approach: "counts", "betweeness", or "closeness".    |
| `p_prior`               | Numeric scalar. Proportion adjustment for subsequent stages.                    |

### 
